Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-13 paper/main.tex
backing up description of fig 6 results

When we examined the data at the level of individual participants
(Fig.~\ref{fig:clustering-scatterplots}), a clearer story emerged.

>>>>

When we examined the data at the level of individual participants
(Fig.~\ref{fig:clustering-scatterplots}), a clearer story emerged. Within each
order manipulation condition, participants exhibited a range of feature
clustering scores, on both early and late lists
(Fig.~\ref{fig:clustering-scatterplots}A, B). Across every order manipulation
condition, participants who exhibited stronger feature clustering (for their
condition's manipulated feature) recalled more words. This trend held overall
across conditions and participants (early: $r(179) = 0.537, p < 0.001$; late: $
r(179) = 0.492, p = 0.000$) as well as for each condition individually for
early ($r$s $\geq 0.386$, all $p$s $\leq 0.035$) and late ($r$s $\geq 0.462$,
all $p$s $\leq 0.010$) lists. We found no evidence of a condition-level trend;
for example the conditions where participants tended to show stronger
clustering scores were not correlated with the conditions where participants
remembered more words (early: $r(4) = 0.526, p = 0.284$; late: $r(4) = -0.257,
p = 0.623$; see insets of panels A and B). We observed carryover associations
between feature clustering and recall performance
(Fig.~\ref{fig:clustering-scatterplots}C, D). Participants who showed stronger
feature clustering on early lists tended to recall more items on late lists
(across conditions: $r(179) = 0.492, p < 0.001$; all conditions individually:
$r$s $\geq 0.462$, all $p$s $\leq 0.010$). Participants who recalled more items
on early lists also tended to show stronger feature clustering on late lists
(across conditions: $r(179) = 0.280, p < 0.001$; all non-visual conditions:
$r$s $\geq 0.445$, all $p$s $\leq 0.014$; color: $r(29) = 0.298, p = 0.103$;
location: $r(28) = 0.354, p = 0.055$). Neither of these effects showed
condition-level trends (early feature clustering versus late recall
probability: $r(4) = -0.299, p = 0.565$; early recall probability versus late
feature clustering: $r(4) = 0.400, p = 0.432$). We also looked for associations
between feature clustering and temporal clustering. Across every order
manipulation condition, participants who exhibited stronger feature clustering
also exhibited stronger temporal clustering. For early lists
(Fig.~\ref{fig:clusteringfig:clustering-scatterplots}E), this trend held
overall ($r(179) = 0.924, p < 0.001$), for each condition individually (all
$r$s $\geq 0.822$, all $p$s $< 0.001$), and across conditions ($r(4) = 0.964, p
= 0.002$). For late lists
(Fig.~\ref{fig:clusteringfig:clustering-scatterplots}F), the results were more
variable (overall: $r(179) = 0.348, p = 0.000$; all non-visual conditions: $r$s
$\geq 0.382$, all $p$s $\leq 0.037$; color: $r(29) = 0.453, p = 0.011$;
location: $ r(28) = 0.190, p = 0.314$; across-conditions: $r(4) = -0.036, p =
0.945$). While less robust than the carryover associations between feature
clustering and recall performance, we also observed some carryover associations
between feature clustering and temporal clustering
(Fig.~\ref{fig:clusteringfig:clustering-scatterplots}G, H). Participants who
showed stronger feature clustering on early lists trended towards showing
stronger temporal clustering on later lists (overall: $r(179) = 0.301, p <
0.001$; for individual conditions: all $r$s $\geq 0.297$, all $p$s $\leq
0.111$; across conditions: $ r(4) = 0.107, p = 0.840$). And participants who
showed stronger temporal clustering on early lists trended towards showing
stronger feature clustering on later lists (overall: $r(179) = 0.579, p <
0.001$; all non-visual conditions: $r$s $\geq 0.323$, all $p$s $\leq 0.082$;
visual conditions: $r$s $\geq 0.089$, all $p$s $\leq 0.632$; across conditions:
$r(4) = 0.916, p = 0.010$).
